---
title: "MCQ scoring and scaling"
output: html_document

params:
  modcode: NA
  scored: NA
  aplus: NA
  pass: NA
  

---




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(numform)
library(kableExtra)

library(tidyverse)

# convert raw data to raw totals per student
dist<-params$scored %>% group_by(SRN) %>% summarise(score=sum(score))

pass<-params$pass
aplus<-params$aplus
scored<-params$scored

# convert raw scores to grade using aplus and pass
  points<-aplus-pass  # what is the gap between 42 and 100
   binwidth<-round(points/11,0)    # how wide are the 11 bins

   dist<-dist %>% mutate(grade=case_when(
      score<pass ~ 38,   # if below pass, grade is 38
      score<pass + binwidth ~ 42,
      score<pass + 2*binwidth ~ 45,
      score<pass + 3*binwidth ~ 48,
      score<pass + 4*binwidth ~ 52,
      score<pass + 5*binwidth ~ 55,
      score<pass + 6*binwidth ~ 58,
      score<pass + 7*binwidth ~ 62,
      score<pass + 8*binwidth ~ 65,
      score<pass + 9*binwidth ~ 68,
      score<pass + 10*binwidth ~ 77,
      score<aplus ~ 88,
      
      TRUE ~ 100
   ))

gtable<-tibble(Grade=c("F+", "D-", "D", "D+", "C-", "C", "C+", "B-", "B", "B+", "A-", "A", "A+"),
                  Min=c(0,pass,pass+binwidth,pass+2*binwidth,
                        pass+3*binwidth, pass+4*binwidth,pass+5*binwidth,
                        pass+6*binwidth, pass+7*binwidth,pass+8*binwidth,
                        pass+9*binwidth, pass+10*binwidth,aplus) 
   )
            
   



# Conversion for grades to letters, linear categories 1-15, and classes
CATEGORICAL=tibble(Grade=c(0, 15 , 25, 38, 42, 45, 48, 52, 55, 58, 62, 65, 68, 77, 88, 100),
                   Category=0:15, 
                   Letter=c("N","F-", "F", "F+", "D-", "D", "D+", "C-", "C", "C+", "B-", "B", "B+", "A-", "A", "A+"),
                   Class=c("Zero","Fail", "Fail", "Fail", "3rd", "3rd", "3rd", "2:II", "2:II", "2:II", "2:I", "2:I", "2:I", "1st", "1st", "1st"),
                   MClass= c("Zero","Fail", "Fail", "Fail", "Fail", "Fail", "Fail", "Pass", "Pass", "Pass", "Merit", "Merit", "Merit", "Dist", "Dist", "Dist")) 


       



#### MARKDOWN ----

```
### Processing marks for `r params$modcode`.
There were `r nrow(scored)` answers received
 from `r length(unique(scored$SRN))` students 
 answering `r length(unique(scored$name))` items.
 
### Raw total correct
```{r plot_raw, echo=FALSE, message=FALSE, warning=FALSE}
dist %>% ggplot(aes(x=score))+geom_bar()
```

The Module Leader identified `r pass` as the minimum total required to Pass (D-) and `r aplus` as the minimum total required for A+.

The other grades were allocated equal bin widths of `r binwidth` between these two values, with the remainder allocated to A grades.

`r  kable_styling(kable(t(gtable),  align=c("r","l"), caption="Minimum total correct required for each Grade"),full_width=F)` 

### Grade distribution

```{r plot_grades, echo=FALSE, message=FALSE, warning=FALSE}
# create grade plot labelled with N and percent
pct_format <- scales::percent_format(accuracy = .1)
    
dist %>% ggplot(aes(x=grade))+
       geom_bar() +
       geom_text(
       aes(
          label = sprintf(
             '%d (%s)',
             ..count..,
             pct_format(..count.. / sum(..count..))
          )
       ),
       stat = 'count',
       nudge_y = 1,
       colour = 'royalblue',
       size = 3)


```




Produced : `r format(Sys.time(), "%a %b %d %X %Y")`

